TUGAS POLINOMIAL CHAPTER 15

### 2021-10-12 Semester I/Pemrograman dalam Sains/Minggu VIII/pr.Rmd
done alhamdulillah

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.retina = 10,fig.cap = "Gambar 15.2"}
f = function(x){3*x^5 + 6}
a = -5
b = 5
delta = .05
gambar_fx(f,a,b,delta)
```

@@

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.retina = 10,fig.cap = "Gambar 15.3"}
f = function(x){2*x^6 - 1.5*x^5 + 5*x^4 - 6.5*x^3 + 6*x^2 - 3*x + 4.5}
a = -5
b = 5
delta = .05
gambar_fx(f,a,b,delta)
```

>>>>

```{r,include=FALSE,message=FALSE,warning=FALSE,fig.retina = 10,fig.cap = "Gambar 15.2"}
f = function(x){3*x^5 + 6}
a = -5
b = 5
delta = .05
gambar_fx(f,a,b,delta)
```

@@

```{r,include=FALSE,message=FALSE,warning=FALSE,fig.retina = 10,fig.cap = "Gambar 15.3"}
f = function(x){2*x^6 - 1.5*x^5 + 5*x^4 - 6.5*x^3 + 6*x^2 - 3*x + 4.5}
a = -5
b = 5
delta = .05
gambar_fx(f,a,b,delta)
```
